### 2014-09-19 fundamentals/impl.tex
moved last sentence back to second p

A key compontent of the \Cyclus kernel architecture is the ability for
implementations of actors in a given simulation to be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be comparied to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle. Interchangability is accomplished by providing
APIs that define agent-to-agent interaction and agent-to-environment
interaction, primarily through the \Class{Agent} and \Class{Trader} interfaces.

The \Class{Agent} interface provides a notion of parent-child hierarchichal
relationship, where parents can choose to \textit{build} child agents and
\textit{decommission} child agents. The \Class{Trader} interface allows
agent-agent interaction through the trading of \Class{Resource}s. Usabe
archetypes in a \Cyclus simulation must implement the \Class{Agent} interface
and may optionally implement the \Class{Trader} interface. For example, a
\Class{Region} implements only the \Class{Agent} interface, whereas a
\Class{Facility} implements both the \Class{Agent} and \Class{Trader} interface,
allowing any \Class{Facility} to trade with another \Class{Facility}.

>>>>

A key compontent of the \Cyclus kernel architecture is the ability for
implementations of actors in a given simulation to be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be comparied to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

Interchangability is accomplished by providing APIs that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. The \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. The \Class{Trader} interface allows agent-agent interaction through the
trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
implement the \Class{Agent} interface and may optionally implement the
\Class{Trader} interface. For example, a \Class{Region} implements only the
\Class{Agent} interface, whereas a \Class{Facility} implements both the
\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
trade with another \Class{Facility}.
